Quantum Walks and Application to Quantum Money

### 2025-04-03 main.tex
presentation updated
main.tex updated

\subsubsection*{4. Toffoli Gate (CCNOT Gate)}
\textbf{Operation:} A three-qubit gate that flips the state of the target qubit if both control qubits are in the state $|1\rangle$. \\
\textbf{Matrix Representation:}
\[
CCNOT =
\begin{bmatrix}
1 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\
0 & 1 & 0 & 0 & 0 & 0 & 0 & 0 \\
0 & 0 & 1 & 0 & 0 & 0 & 0 & 0 \\
0 & 0 & 0 & 1 & 0 & 0 & 0 & 0 \\
0 & 0 & 0 & 0 & 1 & 0 & 0 & 0 \\
0 & 0 & 0 & 0 & 0 & 1 & 0 & 0 \\
0 & 0 & 0 & 0 & 0 & 0 & 0 & 1 \\
0 & 0 & 0 & 0 & 0 & 0 & 1 & 0
\end{bmatrix}
\]

@@

\section*{Groups and Characters}

\section{Abelian Groups}

@@

\subsection{Characters of Abelian Groups}
Let \( G \) be an abelian group. A function

@@

\section*{Number of Characters in a Finite Abelian Group}

@@

\section*{Character Group}

@@

\section{Quantum Fourier Transform}

@@

\[
F_G = \frac{1}{\sqrt{|G|}} \sum_{x \in G} \sum_{y \in \hat{G}} \chi_y(x) | y \rangle \langle x |
\]

@@

\begin{itemize}
    \item \( \hat{G} \) is a complete set of characters of \( G \).
    \item \( \chi_y(x) \) denotes the \( y \)th character of \( G \), evaluated at \( x \).
    \item \( |x\rangle \) and \( |y\rangle \) are quantum states corresponding to elements of \( G \) and its dual group \( \hat{G} \).
\end{itemize}

@@

\subsection{QFT Over \( \mathbb{Z}_{2^n} \)}

@@

\subsection*{Cayley graphs}

@@

\section*{Definition of Cayley Graphs}

A \textit{Cayley graph} is a graph that encodes the structure of a group with respect to a chosen generating set. Formally, let \( G \) be a group and \( S \) be a subset of \( G \) that serves as a generating set, meaning every element of \( G \) can be expressed as a finite product of elements from \( S \). The Cayley graph \( \Gamma(G, S) \) is defined as follows. The vertex set of the graph consists of the elements of \( G \), where each vertex corresponds to a unique group element. The edge set is constructed by drawing a directed edge from vertex \( g \) to vertex \( gs \) for each \( g \in G \) and \( s \in S \). If the generating set \( S \) is symmetric, meaning that whenever \( s \in S \), its inverse \( s^{-1} \) is also in \( S \), then the Cayley graph is undirected; otherwise, it is a directed graph.
For example, For the cyclic group \( G = \mathbb{Z}_n = \{0,1,2,\dots, n-1\} \) with the generating set \( S = \{\pm 1\} \), the Cayley graph forms a cycle graph. In this graph, each vertex \( j \) is connected to \( j+1 \mod n \) and \( j-1 \mod n \), creating a cyclic structure.\\

@@

\section*{Discrete-Time Quantum Walk on Cayley Graphs}

@@

Each state is represented as:
\[
|\psi\rangle = \sum_{g \in G} \sum_{s \in S} \alpha_{g,s} |g\rangle \otimes |s\rangle,
\]
where \( |g\rangle \) is the vertex state and \( |s\rangle \) represents the coin state.

@@

We now briefly outline the quantum money construction from \cite{zhandry2024quantum}, which is based on abelian group actions. Let $\{(G_\lambda, X_\lambda, *)\}_{\lambda \in J}$, where $J \subset \N$, be a collection of cryptographic group actions for abelian groups $G_\lambda$, and let $x_\lambda \in X_\lambda$ be a fixed element. The $\gen$ and $\ver$ algorithms are as follows:
\begin{itemize}
\item $\gen(1^\lambda)$. Begin with the state $\ket{0}\ket{x_\lambda}$, and apply the quantum Fourier transform over $G_\lambda$ to the first register producing the superposition
    \[ \frac{1}{\sqrt{\abs{G_\lambda}}} \sum_{g \in G_\lambda} \ket{g}\ket{x_\lambda}. \]
    Next, apply the unitary transformation $\ket{h}\ket{y} \mapsto \ket{h}\ket{h * y}$ to this state, followed by the quantum Fourier transform on the first register. This results in
    \[ \frac{1}{\abs{G_\lambda}} \sum_{h \in G_\lambda} \sum_{g \in G_\lambda} \chi(g, h) \ket{h}\ket{g * x_\lambda} = \frac{1}{\sqrt{\abs{G_\lambda}}} \sum_{h \in G_\lambda} \ket{h} \ket{G^{(h)} * x_\lambda} \]
    where,
    \[
    \ket{G^{(h)}*x_\lambda} = \frac{1}{\sqrt{|G_\lambda|}}\sum_{g \in G_\lambda}\chi(g,h)\ket{g*x_\lambda}
    \]
    . Measure the first register to obtain a random $h \in G_\lambda$, collapsing the state to $\ket{G^{(h)} * x_\lambda}$. Return the pair $(h, \ket{G^{(h)} * x_\lambda})$.

@@

Given a state of the form $\ket{\Z_N^{(h)} * x}_H$, we demonstrate how the value of $h$ can be extracted using continuous-time quantum walks. For any $u \in \Z_N$, consider the Cayley graph $\Gamma = (\Z_N, E)$ generated by $Q = {-u, u}$, as introduced in Section \ref{sec:ga-qwalk}. Let $A$ denote the adjacency matrix of $\Gamma$. The eigenvectors of $A$ are given by $\ket{\Z_N^{(h)} * x}$, with corresponding eigenvalues $\lambda_h = 2\cos(2\pi uh / N)$ for each $h \in \Z_N$. According to Theorem \ref{thm:sparse-sim} and the discussion that follows, the unitary evolution operator $W = e^{iAt}$ can be simulated efficiently to exponential precision. To proceed, we first state the following lemma.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\bibliographystyle{plain}
\bibliography{references}

>>>>

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section*{Groups and Characters}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Abelian Groups}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Characters of Abelian Groups}
Let \( G \) be an abelian group. A function

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section*{Number of Characters in a Finite Abelian Group}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section*{Character Group}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Quantum Fourier Transform}

@@

\[
F_G = \frac{1}{\sqrt{|G|}} \sum_{x \in G} \sum_{y \in \hat{G}} \chi(y,x) | y \rangle \langle x |
\]

@@

\begin{itemize}
    \item \( \hat{G} \) is a complete set of characters of \( G \).
    \item \( \chi(y,x) \) denotes the \( y \)th character of \( G \), evaluated at \( x \).
    \item \( |x\rangle \) and \( |y\rangle \) are quantum states corresponding to elements of \( G \) and its dual group \( \hat{G} \).
\end{itemize}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{QFT Over \( \mathbb{Z}_{2^n} \)}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{Cayley graphs}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section*{Definition of Cayley Graphs}

A \textit{Cayley graph} is a graph that encodes the structure of a group with respect to a chosen generating set. Formally, let \( G \) be a group and \( Q \) be a subset of \( G \) that serves as a generating set, meaning every element of \( G \) can be expressed as a finite product of elements from \( Q \). The Cayley graph \( \Gamma(G, Q) \) is defined as follows. The vertex set of the graph consists of the elements of \( G \), where each vertex corresponds to a unique group element. The edge set is constructed by drawing a directed edge from vertex \( g \) to vertex \( gq \) for each \( g \in G \) and \( q \in Q \). If the generating set \( Q \) is symmetric, meaning that whenever \( q \in Q \), its inverse \( q^{-1} \) is also in \( Q \), then the Cayley graph is undirected; otherwise, it is a directed graph.
For example, For the cyclic group \( G = \mathbb{Z}_n = \{0,1,2,\dots, n-1\} \) with the generating set \( Q = \{\pm 1\} \), the Cayley graph forms a cycle graph. In this graph, each vertex \( j \) is connected to \( j+1 \mod n \) and \( j-1 \mod n \), creating a cyclic structure.\\

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section*{Discrete-Time Quantum Walk on Cayley Graphs}

@@

Each state is represented as:
\[
|\psi\rangle = \sum_{g \in G} \sum_{q \in Q} \alpha_{g,q} |g\rangle \otimes |q\rangle,
\]
where \( |g\rangle \) is the vertex state and \( |q\rangle \) represents the coin state.

@@

We now briefly outline the quantum money construction from \cite{zhandry2024quantum}, which is based on abelian group actions. We will the $\comph$ algorithm:
\paragraph{The $\comph$ Algorithm.}
Given access to the state $\ket{G^{(h)} * x}$, one can efficiently recover the value of $h$ via a quantum algorithm. In particular, there exists a unitary transformation that maps
\[
\ket{G^{(h)} * x} \ket{0} \mapsto \ket{G^{(h)} * x} \ket{h},
\]
leveraging the technique of \textit{phase kickback}. The process proceeds as follows:

Begin with the state $\ket{G^{(h)} * x} \ket{0}$ and apply the quantum Fourier transform (QFT) to the second register. Then apply the unitary operator
\[
\sum_{k \in G} U_k \otimes \ket{k}\bra{k}
\]
to both registers. This operation encodes the character information into the phase, resulting in the state
\[
\frac{1}{\sqrt{\abs{G}}} \sum_{k \in G} \ket{G^{(h)} * x} \chi(-k, h) \ket{k}.
\]
Finally, applying the inverse QFT to the second register disentangles the phase and reveals $h$, yielding the final state $\ket{G^{(h)} * x} \ket{h}$.

\vspace{0.5cm}
Let $\{(G_\lambda, X_\lambda, *)\}_{\lambda \in J}$, where $J \subset \N$, be a collection of cryptographic group actions for abelian groups $G_\lambda$, and let $x_\lambda \in X_\lambda$ be a fixed element. The $\gen$ and $\ver$ algorithms are as follows:
\begin{itemize}
\item $\gen(1^\lambda)$. Begin with the state $\ket{0}\ket{x_\lambda}$, and apply the quantum Fourier transform over $G_\lambda$ to the first register producing the superposition
    \[ \frac{1}{\sqrt{\abs{G_\lambda}}} \sum_{g \in G_\lambda} \ket{g}\ket{x_\lambda}. \]
    Next, apply the unitary transformation $\ket{h}\ket{y} \mapsto \ket{h}\ket{h * y}$ to this state, followed by the quantum Fourier transform on the first register. This results in
    \[ \frac{1}{\abs{G_\lambda}} \sum_{h \in G_\lambda} \sum_{g \in G_\lambda} \chi(g, h) \ket{h}\ket{g * x_\lambda} = \frac{1}{\sqrt{\abs{G_\lambda}}} \sum_{h \in G_\lambda} \ket{h} \ket{G^{(h)} * x_\lambda} \]
    where,
    \[
    \ket{G^{(h)}*x_\lambda} = \frac{1}{\sqrt{|G_\lambda|}}\sum_{g \in G_\lambda}\chi(g,h)\ket{g*x_\lambda}
    \]
    . Measure the first register to obtain a random $h \in G_\lambda$, collapsing the state to $\ket{G^{(h)} * x_\lambda}$. Return the pair $(h, \ket{G^{(h)} * x_\lambda})$.

@@

Given a state of the form $\ket{\Z_N^{(h)} * x}_H$, we demonstrate how the value of $h$ can be extracted using continuous-time quantum walks. For any $u \in \Z_N$, consider the Cayley graph $\Gamma = (\Z_N, E)$ generated by $Q = {\{-u, u}\}$. Let $A$ denote the adjacency matrix of $\Gamma$. The eigenvectors of $A$ are given by $\ket{\Z_N^{(h)} * x}$, with corresponding eigenvalues $\lambda_h = 2\cos(2\pi uh / N)$ for each $h \in \Z_N$. According to Theorem \ref{thm:sparse-sim} and the discussion that follows, the unitary evolution operator $W = e^{iAt}$ can be simulated efficiently to exponential precision. To proceed, we first state the following lemma.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\newpage
\bibliographystyle{plain}
\bibliography{references}
